A quantitative framework for investigating the reliability of network construction

### 2018-01-18 manuscript/CI_interactions.tex
my read-through edits. Need to make Box 2

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown. This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. What it implies is that 'no interaction' is the most likely ø¨†come when the species do co-occur, but there is nonetheless a substantial chance that the two species \emph{could} interact. In contrast, in the situation where $k>0$, i.e., when we are sure that an interaction is feasible, we still cannot be sure that absence of interactions is caused by $L=0$. Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species may never have been documented as co-occuring). Consequently, the uncertainty in the estimation of $\lambda$ might be considerable. In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all observations, we can use a Bayesian approach to supplement what data we do have with other sources of information.

@@

          In absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$. The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.

@@

          In the literature of ecological networks there is a solid collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,
          % [[from the literature or from our network? Has to be from the literature - if it was our network we'd know way more than just C]] 
          then the beta parameters could be computed as follows using the method of moments:

@@

      \subsubsection*{Trait-matching function}.

@@

          As a fourth and final approach to obtain the prior distribution of $\lambda$, we envisage using the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available. 
          In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$. There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to ~\citep{Bartomeus2016} and~\citep{Weinstein2017} for recent reviews about this topic. Note that in this case the prior might not be beta distributed and numerical methods might be required to compute the posterior distribution.

@@

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. Then, the maximum likelihood estimate of the interaction probability (Box 1) is simply $\lambda_{MLE} = 3/10 = 0.3$.

@@

    then species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species) and
    we can use this to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:

@@

    The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data. We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$. With some simple R code (function ``calculate\_parameters", \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63. Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S2}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026. Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance. We may also wish to calculate a credible interval (analogous to the frequentist confidence interval). This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S2}). In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).

    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e. $k=0$. The question is then ``what is the probability that these two species do not interact''? Since it is not possible to prove that the two species could never interact (strictly speaking, in this approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$). We call this threshold probability $\lambda*$. We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$. The function ``plot\_precision" in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}). Note the special case where there is no observation of the two species co-occurring, $n = 0$.  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. To that end, we use data from another well-described system of \emph{Salix}, gallers, and natural enemies~\citep{Barbour2016,Barbour2016Dryad}. We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species, but stress that this difference is unlikely to be critical for our purposes. Our interest in specifically in what information can be gained from the extensive sampling of \emph{Salix}, gallers, and natural enemies across Europe and what even such thorough sampling does not reveal; the similar but much smaller system in the United States is merely a starting point from which to obtain somewhat reasonable priors. To do this, we estimated frequencies of  \emph{S. hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code). Specifically, we obtain prior parameters $\alpha$=2.51 and $\beta$=1.89. For the galler-natural enemy component of the network, the corresponding prior parameters are $\alpha$=1.34, $\beta$=9.49. We are then able to use these prior parameters to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed, we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S2} for R implementation). For the \emph{Salix}-galler network, the prior distribution we obtained was: $\bar\lambda$=0.570, var($\lambda$)=0.056. The prior distribution for the galler-natural enemy network was $\bar\lambda$=0.124, var($\lambda$)=0.010. This is consistent with the prior data, where the average interaction probability based on the degree distributions of \emph{Salix} genotypes and gallers was 0.562 and that for gallers and natural enemies was 0.122. These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-natural enemy networks, respectively) - a discrepancy which may reflect the differences in scale between the network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and the extensive network of~\citet{Kopelke2017} which contains tens of \emph{Salix}, galler, and natural enemy species, with the insects representing many different families.

      For a pair of species where some co-occurrences were observed, we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs; thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$. As the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
      $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
      $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network. Thus, for species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow. In other words, we could establish with high certainty that the species will never interact. However, for most pairs of species $i$ and $j$, the species did not co-occur at many sites and our posterior mean and variance retain some of the influence of the prior. Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).  The 95\% credible interval around the estimate of $\lambda$ also shrinks with increasing sample sizes, from (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring to (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction.

@@

      Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function plot\_precision in~\emph{Appendix S2}). Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively. Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds. In fact, only three \emph{Salix}-galler pairs and 31 pairs of gallers and their natural enemies were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1. No pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling. For all we know, most links absent from current descriptions of network structure may be so not because the species do not interact, but because we have not sampled deeply enough to detect them.

@@

    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A). Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%. There are two possible explanations for this discrepancy: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%. As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like "training data"?]]

@@

  Real interaction networks vary~\citep{}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions. In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions, and to partition it into its individual components: interaction uncertainty, process uncertainty and detection uncertainty. The patters unveiled offer tangible recommendations for improved descriptors of ecological interactions. First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction. To counter these establish the true absence of interactions will then require comparatively large sample size – on the order of xxx. Second, xxxx. Third, xxxx. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies. All code used in the paper is made available in the companion supplementary material.

@@

    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits. Each site visit can be considered as a network in its own right and an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
    \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring, and for species that did occur the number of co-occurrences was generally low (mean=4.24, var=36.3 for \emph{Salix}-galler pairs; mean=3.87, var=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). For those species which interacted when co-occurring, the incidence of interaction was also low (mean=12.0, var=155 for \emph{Salix}-galler pairs; mean=4.04, var=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at all. Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F). 
  \caption{\emph{Salix} dataset}
  \label{box1}
\end{floatbox}

%DG: be careful : occurrence, not occurance on the figures
    \begin{figure}
      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset. For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10). Here we show a histogram of the number of pairs of species observed co-occurring at least once. 3986 \emph{Salix}-galler and 9794 galler-enemy pairs were never observed co-occurring: these pairs are omitted from the histogram. \textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting. Here we show a histogram of the number of observed interactions within pairs of co-occurring species. \textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. Most \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction. In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
      \end{figure}

>>>>

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown. This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$) but still cannot be sure of the cause if the interaction is not observed at some sites/times (i.e., we cannot say why $k<n$). There may be local constraints ($X=0$) or we might simply not observe the interaction in every sample ($D<1$).

  Second, where the number of samples $n$ is very low (some pairs of species may never have been documenting as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement what data we do have with other sources of information.

@@

          In the absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$. The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.

@@

          The ecological network literature boasts a solid collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,
          % [[from the literature or from our network? Has to be from the literature - if it was our network we'd know way more than just C]] 
          then the beta parameters could be computed as follows using the method of moments:

@@

      \subsubsection*{Trait-matching function}

@@

          As a fourth and final approach to obtain the prior distribution of $\lambda$, we envisage using the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available. 
          In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$. There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic. Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.

@@

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability (Box~\ref{Box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.

@@

    Species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species). We can combine the normalised degree of $i$ with the normalised degrees of its interaction partners to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:

@@

    The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data. We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$. With some simple R code (function ``calculate\_parameters", \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63. Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S2}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026. Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance. We may also wish to calculate a credible interval (analogous to the frequentist confidence interval). This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S2}). In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).

    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e. $k=0$. The question is then ``what is the probability that these two species do not interact''? Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$). We call this threshold probability $\lambda*$. We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$. The function ``plot\_precision" in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}). Note the special case where there is no observation of the two species co-occurring, $n = 0$.  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. To that end, we use data from another well-described system of \emph{Salix}, gallers, and natural enemies~\citep{Barbour2016,Barbour2016Dryad}. We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species, but stress that this difference is unlikely to be critical for our purposes. Our interest is specifically in what information can be gained from the extensive sampling of \emph{Salix}, gallers, and natural enemies across Europe; the similar but much smaller system in the United States is merely a starting point from which to obtain somewhat reasonable priors. To obtain these priors, we estimated frequencies of  \emph{S. hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code). Specifically, we obtain prior parameters $\alpha$=2.51 and $\beta$=1.89. For the galler-natural enemy component of the network, the corresponding prior parameters are $\alpha$=1.34, $\beta$=9.49. We are then able to use these prior parameters to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S2} for R implementation). For the \emph{Salix}-galler network, the prior distribution we obtained was: $\bar\lambda$=0.570, var($\lambda$)=0.056. The prior distribution for the galler-natural enemy network was $\bar\lambda$=0.124, var($\lambda$)=0.010. This is consistent with the prior data, where the average interaction probability based on the degree distributions of \emph{Salix} genotypes and gallers was 0.562 and that for gallers and natural enemies was 0.122. These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-natural enemy networks, respectively) - a discrepancy which may reflect the differences in scale between the network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and the extensive network of~\citet{Kopelke2017} which contains tens of \emph{Salix}, galler, and natural enemy species, with the insects representing many different families.

      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$. As the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become 
      $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
      $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network. Both distributions are very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

      For most pairs of species $i$ and $j$, however, $n$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n$ (Fig.~\ref{Salix_pdfs}). The 95\% credible interval around the estimate of $\lambda$ also widens as $n$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function plot\_precision in~\emph{Appendix S2}). Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively. Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds. In fact, only three \emph{Salix}-galler pairs and 31 pairs of gallers and their natural enemies were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1. No pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling. For all we know, most links absent from current descriptions of network structure may be so not because the species do not interact, but because we have not sampled deeply enough to detect them.

@@

    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A). Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%. There are two possible explanations for this discrepancy: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%. As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]

@@

  Real interaction networks vary~\citep{}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions. In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions, and to partition it into its individual components: interaction uncertainty, process uncertainty and detection uncertainty. The patters unveiled offer tangible recommendations for improved descriptors of ecological interactions. First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction. To counter these establish the true absence of interactions will then require comparatively large sample size – on the order of 30-50 observations per species pair. Second, where such extensive sampling is not feasible, researchers should still acknowledge the varying levels of confidence surrounding the presence or absence of interactions between different pairs of species. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions (especially interactions that were not observed) should be incorporated in calculations of network properties like connectance or nestedness. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space and with different sampling effort and methodology but will also facilitate comparisons between networks. With confidence intervals around network metrics, we can not only say that one network is more connected than another but also whether the networks are more different than we would expect based on imperfect sampling of interactions. To facilitate these recommendations, we provide all code used in this paper in the supplementary material.

@@

    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits. Each site visit can be considered as a network in its own right or as an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequency of co-occurences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring and, even for species that did occur, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites. Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
  \caption{\emph{Salix} dataset}
  \label{box1}
\end{floatbox}

  This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}).
   In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% credibleinterval spans all values of $\lambda$.
  \caption{Here we derive the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times. As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.}
  \label{box2}
\end{floatbox}

%DG: be careful : occurrence, not occurance on the figures
    \begin{figure}
      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset. For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10). Here we show a histogram of the number of pairs of species observed co-occurring at least once. 3986 \emph{Salix}-galler and 9794 galler-enemy pairs were never observed co-occurring: these pairs are omitted from the histogram. \textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting. Here we show a histogram of the number of observed interactions within pairs of co-occurring species. \textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction. In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
      \end{figure}
